Type Refinements for the Working Class

### 2015-12-19 paper.tex
dead code
fix layout & notation

\paragraph{Case} $\DefRefinesCtxSnoc{\Upsilon}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{quote}
  To know $\FRMemEq{\Upsilon}{\Psi,x:\chi}{N_0}{N_1}{\phi}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{M_0}{M_1}{\Rename{\rho}{\chi}}$, you can conclude
  $\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{\Subst{M_0}{x}{\Rename{\rho}{N_0}}}{\Subst{M_1}{x}{\Rename{\rho}{N_1}}}{\Subst{M_0}{x}{\phi\rho}}$.
  In other words:
  %
  \[
    \infer{
      \FRMemEq{\Upsilon}{\Psi,x:\psi}{N_0}{N_1}{\phi}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}
        .\ \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{M_0}{M_1}{\Rename{\rho}{\chi}}\right)
        \Rightarrow
        \left(%
          \FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{%
            \Subst{M_0}{x}{\Rename{\rho}{N_0}}
          }{%
            \Subst{M_1}{x}{\Rename{\rho}{N_1}}%
          }{\Subst{M_0}{x}{\phi\rho}
          }%
        \right)
      \end{array}
    }
  \]
\end{quote}

@@

% In order
% to make this concrete, let us first define what it takes for a refinement to be
% a type, in the sense of Martin-L\"of---that is, a \emph{value type}. In the
% simple case, where we have a global refinement $\GloballyRefines{\phi}{\tau}$,
% we will say $\GlobalIsValueType{\phi}{\tau}$ when there exists a PER $\psi$ on
% \emph{values} that factors uniquely through $\phi$.

%% In general, we must explain typehood for parametric refinements
%% $\Refines{\Upsilon}{\phi}{\tau}$ as well, however; recall from
%% Remark~\ref{rem:internal} that the definition of $\phi$ consists in a natural
%% transformation
%% $\Of{\phi}{\Hom{\Sets^\SCtx}{\Coyoneda{\Upsilon}}{\PERs{\Exprs_\tau}}}$.
%% Therefore, we say that $\IsValueType{\Upsilon}{\phi}{\tau}$ obtains when there
%% is a unique $\Of{\psi}{\Hom{\Sets^\SCtx}{\Coyoneda{\Upsilon}}{\PERs{\Values_\tau}}}$ such that
%% the following diagram commutes, where
%% $\lambda(\chi)$ is the exponential transpose of $\chi$:
%% \[
%%   \IsValueType{\Upsilon}{\phi}{\tau}
%%   \triangleq
%%   \begin{tikzcd}[sep=huge]
%%     \IMode{\Coyoneda{\Upsilon}\times\Values_\tau^2}
%%       \arrow[r, dotted, "\OMode{\lambda(\psi)}"]
%%       \arrow[d, swap, hook, "\Pair{\ArrId{}}{\IMode{\iota}}"] &
%%     \IMode{\Omega}\\
%%     \IMode{\Coyoneda{\Upsilon}\times\Exprs_\tau^2}
%%       \arrow[swap, ur, "\IMode{\lambda(\phi)}"]
%%   \end{tikzcd}
%% \]
%%
%% Equivalently, and perhaps more simply, we can express value typehood internally
%% in our topos as a presheaf:
%% \[
%%   \Define{
%%     \IsValueType{-}{\phi}{\tau}
%%   }{
%%     \sum_{\psi\in\Pow{\Values_\tau^2}}
%%     \prod_{M,N\in\Values_\tau}
%%     {\phi(M,N)}^{\psi(M,N)}
%%   }
%% \]

>>>>

\paragraph{Case} $\DefRefinesCtxSnoc{\Upsilon}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{quote}
  To know $\FRMemEq{\Upsilon}{\Psi,x:\chi}{N_0}{N_1}{\phi}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{M_0}{M_1}{\Rename{\rho}{\chi}}$, you can conclude
  $\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{\Subst{M_0}{x}{\Rename{\rho}{N_0}}}{\Subst{M_1}{x}{\Rename{\rho}{N_1}}}{\Subst{M_0}{x}{\Rename{\rho}{\phi}}}$.
  In other words:
  %
  \[
    \infer{
      \FRMemEq{\Upsilon}{\Psi,x:\psi}{N_0}{N_1}{\phi}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}
        .\ \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{M_0}{M_1}{\Rename{\rho}{\chi}}\right)\\
        \quad\Rightarrow
        \left(%
          \FRMemEq{\Upsilon'}{\Rename{\rho}{\Psi}}{%
            \Subst{M_0}{x}{\Rename{\rho}{N_0}}
          }{%
            \Subst{M_1}{x}{\Rename{\rho}{N_1}}%
          }{\Subst{M_0}{x}{\Rename{\rho}{\phi}}
          }%
        \right)
      \end{array}
    }
  \]
\end{quote}

@@
